Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-11 paper_I/ms.tex
update results + discussion
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

The on-sky locations of the light curves from Sectors 6 and 7 are
shown in Figure~\ref{fig:lcgalactic}.  Black stars are the field stars
for which we performed photometry, and from which we selected template
stars for TFA, as well as the construction of the PCA eigenvectors.
Blue points are the \numberlcs stars with light curves available from
\stscilink.  Most of the target stars are quite close to the galactic
plane.  Gaps between CCD chips are also visible.  The highly clumped
nature of the target stars is also apparent.

Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of TESS
$T$-band magnitudes for the target stars.  Though most of the targets
are faint, $\approx3\times10^4$ are brighter than $T=13$. The brighter
targets will be more amenable to detailed spectroscopic observtions,
should the need arise.

An HR diagram for the entire sample of CDIPS stars on silicon is shown
in Figure~\ref{fig:hrd} (top).  The sub-sample of stars with measured
positive parallaxes and naive distances less than $1\,{\rm kpc}$ is
also shown (bottom).  About one-third of the stars are in this latter
sample.  Of the close stars, a relatively large fraction come from
\citet{zari_3d_2018}, and are either on the PMS or upper
main-sequence.  The latter set of OBA dwarf stars, while ``younger''
than the typical field dwarf, are likely the least interesting subset
of our target sample from the perspective of age analyses.  In the
entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of
stars are sub-giants, red giants, and helium-burning red-clump stars.

@@

Table~\ref{tbl:s6_lcs} shows the clusters in Sector 6 with the largest
numbers of light curves. The top four clusters are all moving groups
or stellar associations from \citet{dias_proper_2014}: Platais~5,
Platais~6, Mamajek~3, and Collinder~70.  These membership claims
should be regarded with serious skepticism.  For Platais~6,
\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
(1$\sigma$) to exist within the angular radius of the cluster.
Mamajek~3 (= 32$\,$Ori) similarly has only about 50 confirmed members
\citep{bell_32ori_2017}.
Some rich open clusters in the Sector 6 field with many light curves,
and more reliable membership lists include Trumpler~5,
Collinder~69 (the $\lambda$ Orionis cluster), and NGC~2287.

@@

\paragraph{Observed RMS vs magnitude.}
The standard deviation of the TFA-detrended light curves is plotted as
a function of the catalog $T$-band magnitude for CDIPS light curves in
Figure~\ref{fig:rms_vs_mag}.
For the $y$-axis of this plot, we have taken
\begin{equation}
  {\rm RMS} = \left[
    \frac{1}{N-M-1}
    \sum_{i=1}^{N} (f_i - \bar{f})^2
  \right]^{1/2},
\end{equation}
where $f_i$ is the value of the flux at the $i^{\rm th}$ point in the
time-series, $\bar{f}$ is the mean flux, $N$ is the
number of points in the time-series, and $M$ is the number
of template light curves used during TFA detrending.
The correction in the denominator penalizes the natural degree of
overfitting inherent to the TFA algorithm.

The observed RMS (black points) follows the usual shape, with photon
noise dominating from $T=9$ to $T=12$, beyond which the onset of the
``sky'' background changes the overall slope of the curve to be more
steep.  For the brightest stars ($T\lesssim 9$), a ``systematic
floor'' was part of the mission's error budget
\citep{ricker_transiting_2015}, but has not been observed in early
reports of the photometric performance of various aperture photometry
pipelines ({\it e.g.,} the SPOC pipeline \citealt{jenkins_spoc_2010},
the MIT-QLP \citealt{huang_tess_2018}, and \texttt{eleanor}
\citealt{feinstein_eleanor_2019}).  The fact that our light curves for
the brightest stars are above this purported ``floor'', rather than
below it, suggests that our image subtraction techniques could be
introducing some small degree of noise to the light curves of the
brightest stars.  It is also true however that our largest aperture
contains only about 16 pixels, which is sub-optimal for stars brighter
than $T\approx9$ \citep[see][Figure~14]{Sullivan_et_al_2015}.  Since
the brightest stars are not the focus of the present work, we leave
this issue unaddressed for the time being.

Importantly, the faint stars do not noticeably exhibit
the typical effects of crowding at the faint end 
\citep[{\it e.g.},][Figure~5]{feinstein_eleanor_2019}.
In aperture photometry pipelines, stars in very crowded regions typically 
have their flux overestimated relative to the actual number of photons
that fall on silicon.
This leads to systematic underestimates of the uncertainty in the relative 
fluxes, as well as ``flux contamination'' (the reduction in amplitude of say, 
transit signals, due to diluting flux from neighbor stars).
Our method to work around this problem -- using the catalog magnitudes to 
predict the reference flux values, and measuring deviations from these 
reference fluxes on the subtracted images -- seems to be performing well.

@@

The second change is that we have explicitly included the
estimated noise contribution from unresolved faint stars.  The
brightness of the diffuse sky is dominated by different sources at
different wavelengths.  For instance, the CMB is most important in
the microwave, and thermal radiation from dust grains in the solar
system (zodiacal light) is dominant in the far infra-red
\citep{leinert_1997_1998}.  In the TESS-band, both zodiacal light and
faint stars can play a role, depending on the line of sight under
consideration. The zodiacal light is brightest near the ecliptic
plane, and the faint star background is brightest near the galactic
plane (and towards the galactic center).  
When performing pre-launch noise estimates,
\citet{winn_background_2013}
estimated the photon-counts from each component.
His zodiacal light model was presented by \citet{Sullivan_et_al_2015},
but the faint star component was not emphasized since the Sullivan
simulations were performed away from the galactic plane.

@@

The relevant quantity needed to calculate the integrated 
photon counts from faint sources
is  $N(<m,l,b)$ --- the number of stars per square arcsecond
brighter than magnitude $m$, along a line of sight with galactic
longitude and latitude $(l,b)$.
To calculate this surface density, \citet{winn_background_2013}
queried the Besan\c con model
\citep{robin_synthetic_2003}  along a grid of galactic sight-lines,
and then converted to $I$-band surface brightnesses.
Fitting a smooth function to the results, \citet{winn_background_2013}
found
\begin{equation}
I\ {\rm mag\ arcsec}^{-2} =
    a_0 + a_1 \left(\frac{|b|}{40^\circ}\right)
    + a_2 \left(\frac{|l|}{180^\circ}\right)^{a_3},
\end{equation}
where the galactic longitude $l$ is measured from $-180^\circ$ to
$180^\circ$, and the empirical coefficients were found to be $a_0 =
18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  The fit was
cautioned to be {\it very approximate}.  It is sensitive to the
threshold used to select ``unresolved'' stars, and likely no more
accurate than 0.5 mag on average.  In regions with exceptionally high
extinction ({\it e.g.}, star forming regions) it is expected to
systematic underestimate the background brightness by an even larger
degree.
Nonetheless, this model for the diffuse sky background seems
to agree reasonably well with the observed trend of standard deviation
versus stellar magnitude.

@@

Beyond the white noise properties of the light curves, the red noise
properties are also important. 
In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
raw and TFA-filtered light curves.
The raw light curves have substantial systematic red noise; 
their average autocorrelation, evaluated at various time lags, is
positive.
The TFA-filtered light curves are much closer to gaussian~--~the
average autocorrelation between any two points in these light curves
is close to zero.
However, the average TFA-filtered light curve is not {\it exactly}
gaussian.
At time lags of a few hours or less, there is some excess power.
This suggests that additional detrending may be
necessary to maximize the effectiveness of planet searches (or the discovery of
any other signals via matched-filter techniques).

@@

The light curves provide an opportunity to study many types of
variables, including pulsating stars, rotators, eclipsing binaries,
and transiting planets.
A few hand-picked examples are shown in Figure~\ref{fig:quilt}.
The sources\footnote{
	Top-left to bottom-right:
	3064530810048196352, 
	3080104185367102592, 
	3027361888196408832,
	3125738423345810048,
	3326715714242517248,
	3064487241899832832,
	3024952755135530496,
	2949587413510194688, 
	5274902193830445312 
} were identified by calculating Lomb-Scargle and transit-least
squares periodograms for a subset of the light curves, and inspecting
the peaks with the greatest power
\citep{lomb_1976,scargle_studies_1982,kovacs_box-fitting_2002,vanderplas_periodograms_2015,hippke_TLS_2019}.
We calculated the periodograms using
\texttt{astrobase}.
Our search was extremely cursory~--~a detailed search for transiting
exoplanets will be the subject of future work.
To make the figure, we used the ``PCA2'' light curve for each
star, for simplicity's sake.
To remove outliers, we omitted
data points within 6 hours of the beginning or end of each orbit.
No additional detrending was performed.

The top row of Figure~\ref{fig:quilt} shows two TESS objects of
interest, and an eccentric eclipsing binary.  TOI~496 is a member of M~48 
(NGC~2548,
\citealt{gaia_collaboration_gaia_2018,cantat-gaudin_gaia_2018}), a
$\sim$500 Myr old open cluster \citep{Kharchenko_et_al_2013}.  The
phase variations suggest that it is an eclipsing binary.  TOI~625 is a
potential hot Jupiter orbiting an upper main sequence star, and was
included as a CDIPS target through the \citet{zari_3d_2018}
catalog.  The eccentric EB was claimed by \citet{dias_proper_2014} to
be a member of the $\sim$50 Myr Bochum~5 cluster.  This EB is also of
note because its TFA light curve heavily whitens the out-of-eclipse
signal, leaving an eclipse signal would could be mistaken for a planet 
candidate.  The important
check for potential users of the light curves is of course to consider
light curves with different types of detrending, to prevent these types of
misinterpretations.

@@

In this study, we first collected an all-sky sample of about one
million stars brighter than $G_{\rm Rp}$ of 16.  82\%
of this target star sample are candidate ``cluster'' members, 
where we use the generic ``cluster'' to refer to 
open clusters, stellar associations, and moving groups.
The remaining stars had photometric or astrometric indications of
their youth, and either reside on the pre-main-sequence or upper main
sequence.

We then reduced TESS full frame images taken over the course of about
two months (Sectors 6 and 7; the first fields very close to the
galactic plane).  We performed difference imaging in order to minimize
the complications of the crowded background.  Using forced aperture
photometry, we made light curves for all stars brighter than $G_{\rm
Rp}$ of 13, and went three magnitudes deeper for our target star
sample.  This yielded \numberlcs light curves of candidate young stars
across \numberclusters distinct clusters.

The light curves seem to be limited in precision by photon noise at
the bright end, and by unresolved background stars at the faint end
(Figure~\ref{fig:rms_vs_mag}).
Though the raw light curves show significant red noise, decorrelating
against a set of template stars led to an ensemble of light curves
with very nearly gaussian noise properties 
(Figures~\ref{fig:lc_systematics_dtr} and~\ref{fig:avg_acf}).

@@

We remind the reader that our goal in creating our target catalog was
completeness, rather than fidelity.  To create clean sub-samples, we
advise using the \texttt{CDEXTCAT} header keyword available in the
FITS files, which can be used to merge against the original source
catalog to obtain the membership probabilities claimed by the original
catalog.  Alternatively, simply restricting the targets of interest to
those with provenance from {\it e.g.}, the Gaia-DR2 data is another
way to produce a cleaner sample of cluster targets.

>>>>

Figure~\ref{fig:lcgalactic} shows the on-sky locations of the 
light curves from Sectors 6 and 7.  Black points are the field stars
for which we performed photometry in order to construct
basis vector sets for TFA and PCA.
Blue points are the \numberlcs target stars for which light curves are available at
\stscilink.  Most of the target stars are close to the galactic
plane, and are spatially clustered. 
Gaps between CCD chips are also visible.

Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of TESS
$T$-band magnitudes for the target stars.  Though most of the targets
are faint, $\approx3\times10^4$ are brighter than $T=13$. The brighter
targets will be more amenable to detailed spectroscopic observations,
should the need arise.

An HR diagram for the entire sample of CDIPS stars on silicon is shown
in Figure~\ref{fig:hrd} (top).  The sub-sample of stars with measured
positive parallaxes and naive distances less than $1\,{\rm kpc}$ is
also shown (bottom).  About one-third of the stars are in this latter
sample.  Of the close stars, a relatively large fraction come from
\citet{zari_3d_2018}, and are either on the PMS or upper
main-sequence.  The latter set of OBA dwarf stars, while ``younger''
than the typical field dwarf, are the least interesting subset
of our target sample from the perspective of age analyses.  In the
entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of
stars are sub-giants, red giants, and helium-burning red-clump stars.

@@

Table~\ref{tbl:s6_lcs} lists the clusters in Sector 6 with the largest
numbers of light curves. The top four clusters are all moving groups
or stellar associations from \citet{dias_proper_2014}: Platais~5,
Platais~6, Mamajek~3, and Collinder~70.  These membership claims
should be regarded with skepticism.  For Platais~6,
\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
(1$\sigma$) to exist within the angular radius of the cluster.
Mamajek~3 (= 32$\,$Ori) similarly has only about 50 confirmed members
\citep{bell_32ori_2017}.
Some rich open clusters in the Sector 6 field with
both many light curves and more reliable membership lists
include Trumpler~5,
Collinder~69 (the $\lambda$ Orionis cluster), and NGC~2287.

@@

\paragraph{Observed RMS vs magnitude.}
Figure~\ref{fig:rms_vs_mag} shows
the standard deviation of the TFA-detrended light curves as
a function of the catalog $T$-band magnitude for CDIPS target stars.
For the $y$-axis of this plot, we have taken
\begin{equation}
  {\rm RMS} = \left[
    \frac{1}{N-M-1}
    \sum_{i=1}^{N} (f_i - \bar{f})^2
  \right]^{1/2},
\end{equation}
where $f_i$ is the value of the flux at the $i^{\rm th}$ point in the
time-series, $\bar{f}$ is the mean flux, $N$ is the
number of points in the time-series, and $M$ is the number
of template light curves (principal components) used during TFA (PCA) detrending.
The correction in the denominator is for the overfitting inherent
in any ensemble detrending method.

The observed RMS (black points) follows the usual shape, with source photon
noise dominating from $T=9$ to $T=12$, beyond which the onset of the
``sky'' background changes the overall slope of the curve to be more
steep.  For the brightest stars ($T\lesssim 9$), a ``systematic
floor'' of 60$\,$ppm$\,$hr$^{1/2}$ was part of the mission's error budget
\citep{ricker_transiting_2015}, but has not been observed in early
reports of the photometric performance of various aperture photometry
pipelines ({\it e.g.,} the SPOC pipeline \citealt{jenkins_spoc_2010},
the MIT-QLP \citealt{huang_tess_2018}, and \texttt{eleanor}
\citealt{feinstein_eleanor_2019}).  The fact that our light curves for
the brightest stars are above this purported ``floor'', rather than
below it, suggests that our image subtraction techniques could be
introducing some small degree of noise to the light curves of the
brightest stars.  It is also true however that our largest aperture
contains only about 16 pixels, which is sub-optimal for stars brighter
than $T\approx9$ \citep[see][Figure~14]{Sullivan_et_al_2015}.  Since
the brightest stars are not the focus of the present work, we leave
this issue unaddressed for the time being.

An essential feature of our RMS diagram is that faint stars in
crowded regions are not spuriously driven below theoretical limits.
In aperture photometry pipelines, a star in a crowded region
has its reference flux overestimated relative to the true number of 
photons it contributes (due to contamination from neighbor stars).
As a result, changes in relative flux in the faint star's light curve are 
underestimated, and its RMS is driven low 
\citep[{\it e.g.}, the faint end of][Figure~5]{feinstein_eleanor_2019}.
Our method to work around this issue -- using the catalog magnitudes to 
predict the reference flux values, and measuring deviations from these 
reference fluxes on the subtracted images -- seems to be performing 
as intended.

@@

The second change is that we have explicitly included the
estimated noise contribution from unresolved faint stars.  The
brightness of the diffuse sky is dominated by different sources at
different wavelengths.  For instance, the CMB is most important in
the microwave, and thermal radiation from dust grains in the solar
system (zodiacal light) is dominant in the far infra-red
\citep{leinert_1997_1998}.  In the TESS-band, both zodiacal light and
faint stars can play a role, depending on the line of sight under
consideration. The zodiacal light is brightest near the ecliptic
plane, and the faint star background is brightest near the galactic
plane.  
When performing pre-launch noise estimates,
\citet{winn_background_2013}
estimated the photon-counts from each component.
His zodiacal light model was presented by \citet{Sullivan_et_al_2015},
but the faint star component was not emphasized since the Sullivan
simulations were performed for fields away from the galactic plane.

@@

The relevant quantity needed to calculate the integrated 
photon counts from faint sources
is  $N(<m,l,b)$ --- the number of stars per square arcsecond
brighter than magnitude $m$, along a line of sight with galactic
longitude and latitude $(l,b)$.
To calculate this surface density, \citet{winn_background_2013}
queried the Besan\c con model
\citep{robin_synthetic_2003}  along a grid of galactic sight-lines,
and then converted to $I$-band surface brightnesses.
Fitting a smooth function to the results, \citet{winn_background_2013}
found
\begin{equation}
I\ {\rm mag\ arcsec}^{-2} =
    a_0 + a_1 \left(\frac{|b|}{40^\circ}\right)
    + a_2 \left(\frac{|l|}{180^\circ}\right)^{a_3},
\end{equation}
where the galactic longitude $l$ is measured from $-180^\circ$ to
$180^\circ$, and the empirical coefficients were found to be $a_0 =
18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  The model
is {\it very approximate}.  It is sensitive to the
threshold used to select ``unresolved'' stars, and likely no more
accurate than 0.5 mag on average.  In regions with exceptionally high
extinction ({\it e.g.}, star forming regions) it is expected to
systematic underestimate the background brightness by an even larger
degree.
Nonetheless, this model for the diffuse sky background seems
to agree reasonably well with the observed trend of standard deviation
versus stellar magnitude.

@@

Beyond the white noise properties of the light curves, the red noise
properties are also important. 
In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
raw, PCA, and TFA light curves.
The raw light curves have substantial red noise, and
their average autocorrelation across many time lags is
positive.
The PCA and TFA light curves are much closer to gaussian~--~the
average autocorrelation between any two points in these light curves
is close to zero.
However, the average PCA and TFA light curves are not {\it exactly}
gaussian.
At time lags of a few hours or less, there is some excess power.
This suggests that additional detrending may be
necessary to maximize the effectiveness of planet searches, or the discovery of
any other signals via matched-filter techniques.

@@

The light curves provide an opportunity to study many types of
variables, including pulsating stars, rotators, eclipsing binaries,
and transiting planets.
A few hand-picked examples are shown in Figure~\ref{fig:quilt}.
The sources\footnote{
	Top-left to bottom-right:
	3064530810048196352, 
	3080104185367102592, 
	3027361888196408832,
	3125738423345810048,
	3326715714242517248,
	3064487241899832832,
	3024952755135530496,
	2949587413510194688, 
	5274902193830445312 
} were identified by calculating Lomb-Scargle and transit-least
squares periodograms for a subset of the light curves, and inspecting
the peaks with the greatest power
\citep{lomb_1976,scargle_studies_1982,kovacs_box-fitting_2002,vanderplas_periodograms_2015,hippke_TLS_2019}.
We calculated the periodograms using
\texttt{astrobase}.
Our search was cursory~--~a detailed search for transiting
exoplanets will be the subject of future work.
To make the figure, we used the ``PCA2'' light curve for each
star, for simplicity's sake.
To remove outliers, we omitted
data points within 6 hours of the beginning or end of each orbit.
No additional detrending was performed.

The top row of Figure~\ref{fig:quilt} shows two TESS objects of
interest, and an eccentric eclipsing binary.  TOI~496 is a member of M~48 
(NGC~2548,
\citealt{gaia_collaboration_gaia_2018,cantat-gaudin_gaia_2018}), a
$\sim$500 Myr old open cluster \citep{Kharchenko_et_al_2013}.  The
phase variations suggest that it is an eclipsing binary.  TOI~625 is a
potential hot Jupiter orbiting an upper main sequence star, and was
included as a CDIPS target through the \citet{zari_3d_2018}
catalog.  The eccentric EB was claimed by \citet{dias_proper_2014} to
be a member of the $\sim$50 Myr Bochum~5 cluster.  This EB is also
notable because its TFA light curve heavily whitens the out-of-eclipse
signal, leaving an eclipse signal that could be mistaken for a planet 
candidate.  The relevant lesson
for anyone using the light curves is to verify
that detrending does not introduce or remove signals
that alter the interpretation of the system.

@@

In this study, we collected an all-sky sample of about one
million stars brighter than $G_{\rm Rp}$ of 16.  82\%
of this target star sample are candidate ``cluster'' members, 
where we use the generic ``cluster'' to refer to 
open clusters, stellar associations, and moving groups.
The remaining stars had photometric or astrometric indications of
their youth, and either reside on the pre-main-sequence or upper main
sequence.

We then reduced TESS full frame images taken over the course of about
two months (Sectors 6 and 7; the first fields close to the
galactic plane).  We performed difference imaging in order to 
deal with the complex background.  Using forced aperture
photometry, we made light curves for all stars brighter than $G_{\rm
Rp}$ of 13, and went three magnitudes deeper for our target star
sample.  This yielded \numberlcs light curves of candidate young stars
across \numberclusters distinct clusters.

The light curves seem to be limited in precision by photon-counting noise 
from the target star at
the bright end, and by unresolved background stars at the faint end
(Figure~\ref{fig:rms_vs_mag}).
Though the raw light curves show significant red noise, decorrelating
against a set of template stars led to an ensemble of light curves
with very nearly gaussian noise properties 
(Figures~\ref{fig:lc_systematics_dtr} and~\ref{fig:avg_acf}).

@@

We remind the reader that our goal in creating our target catalog was
completeness, rather than reliability.  To create clean sub-samples, we
advise using the \texttt{CDEXTCAT} header keyword available in the
FITS files, which can be used to merge against the original source
catalog to obtain the membership probabilities claimed by the original
catalog.  Alternatively, simply restricting the targets of interest to
those with provenance from {\it e.g.}, the Gaia-DR2 data is another
way to produce a cleaner sample of cluster targets.
